Uni- and Multivariate Analysis of Dendritic Ca2+ Data

### 2017-07-18 presentation/demo.tex
asd

@@

>>>>

\begin{frame}[fragile]{SVM Specifics}
\begin{itemize}
\item All data are normalized to zero mean and unit variance
\item Crossvalidation is performed to conrol for overfitting
\end{itemize}

@@

\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Presence}
\begin{center}
	\begin{figure}
	%\caption*{todo: tens, improve weights}
      \includegraphics[width=1.0\textwidth]{data_p_tot.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Presence}
Performance on global presence detection: \newline
Mean: 0.68 \newline
Standard deviation: 0.08
\end{frame}

\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
\begin{center}
	\begin{figure}
	%\caption*{todo: tens, improve weights}
      \includegraphics[width=1.0\textwidth]{data_hm_tot.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Global Behavior}
Performance on global presence detection: \newline
Mean: 0.71 \newline
Standard deviation: 0.1
\end{frame}
